%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \documentclass[]{deedy-resume-openfont}

    \begin{document}
    
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \namesection{Pratyush}{Raj}{pratyushraj2f2gmail.com | +916206690294 | Ashish anand enclave, Tupudana, Ranchi, Jharkhand , India | devpost.com/rajpratyush}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Links
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links}
\raggedright
\begin{tabular}{l l}
{{\descript{GitHub} }}\hspace*{6pt}\href{https://www.github.com/rajpratyush}{github.com/rajpratyush}
{{\hspace*{38pt} \descript{Linkedin}}}\hspace*{6pt}\href{https://www.linkedin.com/in/rajpratyush}{linkedin.com/in/rajpratyush}\\
{{\descript{HackerRank} }}\hspace*{6pt}\href{https://www.hackerrank.com/2pratyushraj}{hackerrank.com/2pratyushraj}
{{\hspace*{38pt} \descript{Portfolio}}}\hspace*{6pt}\href{https://devpost.com/rajpratyush}{devpost.com/rajpratyush}\\
\end{tabular}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Education
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\raggedright

    \runsubsection{Cochin University College of Engineering}\descript{| Bachelors of Technology Computer Science Engineering}\hfill \location{Alappuzha, Kerela | July 2017 - May 2022}\\
    GPA: 7.8\\
    \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      %
      %     Experience
      %
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \section{Experience}
      \runsubsection{Two waits}\descript{| TA and Python Instructor}\hfill \location{Delhi | May 2021 – July 2021}
          \begin{tightemize}
  \item Instructed 150+ students of multiple batches to reinforce learning concepts.
\end{tightemize}
          \sectionsep
      \runsubsection{Girl Script Summer of Code}\descript{| Mentor – CoinShift Imaging Box}\hfill \location{March 2021 – June 2021}
          \begin{tightemize}
  \item Helped the participants to how to make their first contribution to the project.
  \item Gave them insights on how to create a Pull request and open up an issue and clarified their doubts.
\end{tightemize}
          \sectionsep
      \runsubsection{Code for Cause}\descript{| Campus Leader}\hfill \location{Feb 2021 – May 2021}
          \begin{tightemize}
  \item Mentored students \& Conducted various workshops.
  \item Undertook Programming Bootcamps and workshops in C and C++ as a campus leader.
  \item Gave talks on open source, guided and motivated students to help them proceed in the world of open source.
\end{tightemize}
          \sectionsep
      \runsubsection{DevScript Winter of Code}\descript{| Project Maintainer - SoDV Detector}\hfill \location{Jan 2021 – Feb 2021}
          \begin{tightemize}
  \item Mentored participants and guided them on making opensource contributions.
\end{tightemize}
          \sectionsep
      \runsubsection{The Sparks Foundation}\descript{| Data Science \& Business Analytics Intern}\hfill \location{Nov 2020 – Dec 2020}
          \begin{tightemize}
  \item Solved the Various tasks related to Data science.
  \item The Exploratory data analysis was carried out and ML models were made on various datasets using various open source libraries.
\end{tightemize}
          \sectionsep
      \runsubsection{MedTourEasy}\descript{| Data Engineering Trainee}\hfill \location{Oct 2020 – Nov 2020}
          \begin{tightemize}
  \item Completed Data Engineering with Google Cloud Specialization.
  \item Implemented the learnings in the practical labs taken over Qwiklabs.
\end{tightemize}
          \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\raggedright
\begin{tabular}{ l l }
\descript{Programming Languages} & {\location{Java, Python, Go, C++, JavaScript, TypeScript}} \\
\descript{Libraries/Frameworks} & {\location{Node, React, Three.js, P5.js, Tensorflow, Flask, Streamlit, Pycaret, JobLib}} \\
\descript{Tools / Platforms} & {\location{Docker, Kubernetes, CI/CD, Google Cloud Platform, Microsoft Azure, Heroku}} \\
\descript{Databases} & {\location{SQL, MongoDB, CockroachDB, Cloud Databases}} \\
\end{tabular}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      %
      %     Projects
      %
      %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \section{Projects / Open-Source}
      \raggedright
      
          \runsubsection{\large{NEST}}
          \descript{| Python, Streamlit, JSON}\hfill \location{https://github.com/rajpratyush/NEST}\\
          A web app for predicting prices of houses using Visual and Textual Features using an optimized Deep
Learning method.\\
          \sectionsep
        
      
          \runsubsection{\large{Neuror}}
          \descript{| Android(Java)}\hfill \location{https://github.com/rajpratyush/Neuror}\\
          - An android app connecting people suffering from autism with their prospective employers considering their
special needs.\\
          \sectionsep
        
      
          \runsubsection{\large{SpaceX}}
          \descript{| MongoDB, React, Express, Node.js, Heroku}\hfill \location{https://github.com/rajpratyush/SpaceX}\\
          A MERN Stack based web app to browse all the space programs launched by SpaceX with their Successful
landing, Successful launch and Year of launch\\
          \sectionsep
        
      
          \runsubsection{\large{SoDV Detector}}
          \descript{| Python}\hfill \location{https://github.com/rajpratyush/Social-Distancing-Detector}\\
          An Application to detect social distancing which can be used to detect people in video streams using
the YOLO object detection.\\
          \sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Awards
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Honors \& Awards}
\begin{tightemize}
\item 2020 EMEA - Code For Good Hackathon Winner organized by:- J. P. Morgan Chase (\\
\item Best use of Google Cloud in Neighbourhood Hacks\\
\item Runner up in Twilio Quest Challenge in Hack Cade\\
\item Domain.com Challenge Winner in Pride Hacks.\\
\item Open Source Contributor. (Microsoft-Graspologic, Matplotlib, PyCaret, Streamlit, GeoPandas, Scikit-Image, dask, Google-Python- Fire, TimeSketch)\\
\item Technical Mentor at Hack UTD: The VII Seas, SF Hacks 2021, HACKaBULL, Uncommon Hacks, Hack-TJ 8.0, Oceania Hacks, Bit camp 2021, Citrus Hacks, Venus Hacks, Hydrangea Hacks, GSB hacks.\\
\item Mentor @MLH\\
\item KVPY Scholar.\\
\end{tightemize}
    \ 
    \end{document}